---
title: "NDVI Peak Dynamics"
author: "Robert Paul, Jeff Stephens"
date: "June 23, 2016"
output: html_document
---
# NDVI Peak Dynamics

This workflow detects the length of time for NDVI to go from baseline to peak over the course of the year. Each pixel is classified with a value reflecting the length of time in the year for NDVI to reach peak greenness.

Notes:
 * Allow options for baseline-to-peak or baseline-to-baseline
 * Site: Harvard Forest
 * UTM Zone 18T
 * Data sources: MODIS (primary), Landsat 8, Phenocam
 * First year used: 2012
 * MODIS product: MOD13Q1
 * MODIS tile: h12v4

## Load libraries
```{r load-libraries}
library(raster)
library(rgdal)
library(rts)
library(RCurl)
library(stringr)
```

## Create functions
```{r functions}
# Raster time series pulled from working directory + data/year/index
make_rts <- function(year = '2012', index = 'ndvi') {
  # Just in case the year is passed as an integer
  year <- as.character(year)
  # **The data directory must be in the current working directory!
  directory <- paste("data", year, index, sep='/')
  # Get the files
  files <- list.files(directory, full.names=TRUE)
  # Pull all the files into a raster stack.
  r <- stack(files)
  # Extract dates from file names and cast as Date objects
  dates <- as.Date(str_extract(files, '[0-9]{4}-[0-9]{2}-[0-9]{2}'))
  # Reference the raster stack with their respective dates and collect them
  # together into a time series
  index_ts <- rts(r, dates)
  # Give the raster time series result
  return(index_ts)
}

```

## Load rasters
```{r load-rasters}

# EVI and NDVI files for the year are moved in their own directory
# e.g. EVI files for 2012 are in data/2012/evi
# Get the time series
ndvi_ts <- make_rts(year = "2012", index = "ndvi")
evi_ts <- make_rts(year = "2012", index = "evi")
```

## Handle clouds
```{r handle-clouds}

```

## Trace/describe NDVI over the year
```{r track-ndvi}

```

## Reclassify the raster based on the NDVI dynamics detected
```{r reclass-based-on-time-series}

```

## Plot the reclassified raster
```{r plot-result}

```

## Show animation of raster
```{r animate-changes}

```
