---
title: "NDVI Peak Dynamics"
author: "Robert Paul, Jeff Stephens"
date: "June 23, 2016"
output: html_document
---
# NDVI Peak Dynamics

This workflow detects the length of time for NDVI to go from baseline to peak over the course of the year. Each pixel is classified with a value reflecting the length of time in the year for NDVI to reach peak greenness.

Notes:
 * Allow options for baseline-to-peak or baseline-to-baseline
 * Site: Harvard Forest
 * UTM Zone 18T
 * Data sources: MODIS (primary), Landsat 8
 * First year used: 2012
 * MODIS product: MOD13Q1
 * MODIS tile: h12v4

## Load libraries
```{r load-libraries}
library(raster)
library(rgdal)
library(rts)
library(RCurl)
```

## Create functions
```{r functions}

```

## Load rasters
```{r load-rasters}
# Download the data if it's not found
if(length(dir("/data")) == 0) {
  setwd("data")
  # Change this to where MRT is installed 
  mrt_path <- "/Users/exnihilo/Applications/bin/"
  ModisDownload(x = 1, h = 12, v = 4, dates=c("2012.01.01", "2012.01.31"), proj=T,proj_type="UTM",utm_zone=18,datum="WGS84", pixel_size=250, MRTpath= mrt_path)
  setwd("../")
}

```

## Make an ordered time series of the rasters
```{r time-series-stack}

```

## Handle clouds
```{r handle-clouds}

```

## Trace/describe NDVI over the year
```{r track-ndvi}

```

## Reclassify the raster based on the NDVI dynamics detected
```{r reclass-based-on-time-series}

```

## Plot the reclassified raster
```{r plot-result}

```

## Show animation of raster
```{r animate-changes}

```
